Reasoning with Language Model is Planning with World Model

### 2024-07-07 nlp-papers/reasoning-via-planning/sections/method.tex
Add LLaMa downliad links

With the definition of state and action, the reasoning process can thus be described as a \roundinlinebox[green]{Markov decision process (MDP):} given the current state $s_{t, t=0, 1, \dots, T}$, e.g., the initial state $s_0$, the LLM (as a reasoning agent) generates an action space by sampling from its generative distribution $a_t \sim p(a | s_t, c)$, where $c$ is a proper prompt (e.g., in-context demonstrations). Once an action is chosen, the world model then predicts the next state $s_{t+1}$ of the reasoning. Specifically, we repurpose the \emph{same} LLM to obtain a state transition distribution $p(s_{t+1} | s_t, a_t, c')$, where $c'$ is another prompt to guide the LLM to generate a state. For instance, in \blocksworld, the LLM (as the world model) generates text $s_{t+1}$ to describe the new configuration of blocks, given previous state $s_{t}$ and the action $a_t$.

>>>>

With the definition of state and action, the reasoning process can thus be described as a \highlight[green]{Markov decision process (MDP): given the current state $s_{t, t=0, 1, \dots, T}$, e.g., the initial state $s_0$, the LLM (as a reasoning agent) generates an action space by sampling from its generative distribution $a_t \sim p(a | s_t, c)$, where $c$ is a proper prompt (e.g., in-context demonstrations). Once an action is chosen, the world model then predicts the next state $s_{t+1}$ of the reasoning. Specifically, we repurpose the \emph{same} LLM to obtain a state transition distribution $p(s_{t+1} | s_t, a_t, c')$, where $c'$ is another prompt to guide the LLM to generate a state. For instance, in \blocksworld, the LLM (as the world model) generates text $s_{t+1}$ to describe the new configuration of blocks, given previous state $s_{t}$ and the action $a_t$}.
